% This document provides the style to be used for a MSc Thesis at the
% Parallel and Distributed Systems group
\documentclass[11pt,twoside,a4paper,openright]{report}

% math packages
\usepackage{amsthm}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}

%\usepackage{subfig}
 \usepackage{floatrow}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[toc,page]{appendix}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx,wrapfig,lipsum}
\usepackage{chngcntr}
\usepackage{tabularx}


% textblocks for title page
\usepackage[absolute]{textpos}
\usepackage{tikz}

% use babel for proper hyphenation
\usepackage[british]{babel}
\bibliographystyle{./bib/myCustom}
%\bibliographystyle{abbrvnat}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{bytefield}
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}
\hypersetup{breaklinks=true}
\urlstyle{same}

% Graphics: different for pdflatex or dvi output, choose one
%%\usepackage[dvips]{graphicx}
%%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{rotating}


% FONT
\usepackage[scaled=.92]{helvet}
%\usepackage{times}

% for url's use "\url{http://www.google.com/}"
\usepackage{url}
\usepackage{hyperref}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = cyan, %Colour for external hyperlinks
  linkcolor    = cyan, %Colour of internal links
  citecolor   = cyan %Colour of citations
}
\usetikzlibrary{shapes,arrows,graphs,positioning,automata,shadows,fit,shapes,decorations.pathreplacing}
\tikzset{
    rotate around with nodes/.style args={#1:#2}{
        rotate around={#1:#2},
        set node rotation={#1},
    },
    rotate with/.style={rotate=\qrrNodeRotation},
    set node rotation/.store in=\qrrNodeRotation,
}
\usepackage{etoolbox}
\usepackage{rotating}

%\appto\appendix{\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}}

% reinstate the correct level for list of tables and figures
%\appto\listoffigures{\addtocontents{lof}{\protect\setcounter{tocdepth}{0}}}
%\appto\listoftables{\addtocontents{lot}{\protect\setcounter{tocdepth}{0}}}

\def\algbackskip{\hskip\dimexpr-\algorithmicindent+\labelsep}
\def\LState{\State \algbackskip}%
% Information that will be filled in at various points in the report
\newcommand{\reportTitle}{Occupancy data driven automatic determination of sensor locations in buildings}
\newcommand{\reportAuthor}{Arpan Govindraju}
\newcommand{\reportEmail}{a.govindaraju@student.tudelft.nl}
\newcommand{\reportUrlEmail}{\href{mailto:\reportEmail}{\reportEmail}}
\newcommand{\reportMSC}{MSc Embedded Systems} %{Embedded Systems}{Computer Engineering}{Computer Science}{Electrical Engineering}
\newcommand{\reportDate}{\today} %TODO: Dit is de datum van uitgifte van final versie aan de afstudeer commissie 
\newcommand{\presentationDate}{9th Sept 2016} %TODO: Dit is de datum van de afstudeerpresentatie 
\newcommand{\graduationCommittee}{
Prof. Dr. K. G. Langendoen (Chair) & TU Delft\\
Dr. Venkatesha Prasad R  & TU Delft\\
Dr. Ashish Pandharipande & Philips Research\\
Dr. Christoph Lofi & TU Delft\\
} % The order of listing the names: Graduation prof, supervisor(s), others ordered by title + alphabetical 
%examples: 


\newcommand{\reportAbstract}{Building automation systems (BAS) are getting extremely popular due to increase in the demand to reduce energy consumption in residential and commercial  buildings as well as for other applications such as ambient assisted living, smart home, and smart living. 
As the number of applications increases, the complexity of the systems also increases making the installation and maintenance much more difficult and involved, thus requiring skilled persons to maintain them. One of the main challenges is generating and updating the location meta-data of the sensors. Location meta-data is the primary input for many applications. Currently the location meta-data is being generated and maintained manually, this process is highly cumbersome and also prone to errors. Erroneous location information can make BAS ineffective. Previous investigations have looked at clustering sensors based on their spatial locations, but not at locating the sensors in the space. In this work we propose an automatic sensor data driven sensor location inferencing system. We reduce the problem of determining the location of sensors to a problem of graph matching using the correlation matrix and grid information. Within graph matching the problem belongs to graph monomorphism type, which is an NP-Complete problem. We make use of \textbf{VF2} algorithm a popular graph matching algorithm in this work. Furthermore, we validate our algorithm with two different real world testbeds. We are able to locate all the sensors accurately for our experimental testbed and for the Tokyo testbed we observe an error in the determination of sensor location for only 3 out of the 43 sensors.
}
\newcommand{\reportKeywords}{TODO KEYWORDS}
%\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
%\counterwithin{definition}{chapter}

% For pdflatex
\pdfinfo{
   /Author (\reportAuthor)
   /Title  (\reportTitle)
   /Keywords (\reportKeywords)
}

\begin{document}

\pagenumbering{alph}
\pagestyle{empty}


% FRONTCOVER
\include{./template/frontcover}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hoffset=1.63cm
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=5in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parindent=1em

% EMPTY PAGE
\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{1}

% TITLE PAGE: page i (hidden)
\include{./template/titlepage}

% GRADUATION DATA AND ABSTRACT: pages ii and iii (hidden)
\include{./template/graduationdata}
%\setcounter{page}{4}

% EMPTY PAGE: page iv
\cleardoublepage

% OPTIONAL QUOTATION: page v
\include{./chapters/quotation}
% EMPTY PAGE: page vi
%\cleardoublepage

% PREFACE: page v
\include{./chapters/preface}
% EMPTY PAGE: page vi
\cleardoublepage

% TABLE OF CONTENTS: starting at page vii

\tableofcontents


\cleardoublepage
\pagestyle{plain}
\pagenumbering{arabic}
\setcounter{page}{1}

% INTRODUCTION: page 1
\include{./chapters/introduction}



% CHAPTERS ... For instance: History/Prior Work, Design/Implementation, Experiments
\include{./chapters/literatureReview}

% CONCLUSIONS AND FUTURE WORK
\include{./chapters/method}
\include{./chapters/TestBed}
\include{./chapters/results}
\include{./chapters/conclusionsandfuturework}


% BIBLIOGRAPHY
%#define SORTED 1
%\bibliographystyle{agsm}
\bibliography{./bib/mycollection}


\begin{appendix}

\include{./chapters/appendix_a}

\end{appendix}

%\appendix

%\include{appendix_a}

\end{document}
