\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}


\vspace{1\baselineskip}

\noindent
Indoor spaces are getting smarter day by day with deployment of huge amount of sensors and actuators. Many applications built for maintenance of the building use the sensor data as inputs to actuate the actuators to perform their function. May it be simple turning on and off of lights based on occupancy or a more critical applications like fire detection and alarming, all need data from the sensors. One important meta-data about the sensor, that is crucial for all theses application is the sensor location. Without which the applications cannot perform effectively. Till now the meta-data is being created and maintained manually, which is a cumbersome process and prone to error. In our work here we propose a method to automatically determine the location of the sensor using the data from the sensors.

This work was carried out at Philips Lighting, Eindhoven. Philips Lighting being a market leader in the field of lighting are actively providing lighting control solutions. This work is aimed to help automate the process of creating and maintaining the meta-data of sensor location and thus aiding faster deployment and easier maintenance of the systems.

Before going to the technical details of the thesis, I would like to thank my supervisor Dr.Ashish Pandharipande(Philips Lighting) for giving me an opportunity to carry out my thesis at Philips Lighting. I would also like to thank him and Dr.David Caicedo Fernandez(Philips Lighting) for critically analyzing my work during our regular weekly meetings and giving me valuable suggestions. My sincere gratitude to my university supervisor Dr.Venkatesh Prasad(TU Delft) for all the support and guidance he provided. I would also like to thank my parents and grandparents for their unconditional love and support during all these years.
I would like to thank all my friends who have tolerated my constant whining and supported me during my tough times.
A special thanks to all the people of FO 52, past and the present who made the stay in Eindhoven so much more pleasant.

\vspace{1\baselineskip}

\noindent
Arpan Goindaraju\\
%\vspace{1\baselineskip}
%\noindent
Eindhoven, The Netherlands\\
%\noindent
\today
